\Title

### 2020-01-15 manuscript/manuscript.tex
Start writing the equivalent sources technique section

@@

\begin{equation}
    \textrm{depth} =
        \textrm{depth_factor} \textrm{mean_distance} + \textrm{static_shift}
\end{equation}

\noindent where the $\textrm{depth_factor}$ and the $\textrm{static_shift}$ are
parameters and the $\textrm{mean_distance}$ is the mean distance to the $k$
nearest source neighbours.

>>>>

The Green's equivalent layer theorem states that any harmonic potential field
generated by any three dimensional physical-property distribution can by
reproduced by a continuous two dimensional surface distribution.
This introduces an ambiguity on the distribution that generates
a potential field: multiple physical-property distributions can generate the
same potential field.
This represents an obstacle for determining the true shape and
physical-property distribution that generates the measured potential field.
Nevertheless this ambiguity can also be exploited for developing preprocessing
techniques like interpolating potential field data.

Approximating the continuous distribution by a finite and discrete density
distribution is the basis of the \emph{equivalent sources technique}
\citep{dampney1969}.
The most common approach is to make use of a set of point masses (the
\emph{equivalent sources}) located beneath the observation points.

Lets consider a set of gravity acceleration measurements $g_z$ on points
$\{\mathbf{p}_1, \ldots, \mathbf{p}_N\}$ and a set of point sources with mass
$\{m_1, \ldots, m_M\}$ located on points
$\{\mathbf{q}_1, \ldots, \mathbf{q}_M\}$.
The point sources must generate the same gravity field as the one measured:

\begin{equation}
    \mathbf{g}(\mathbf{p}) = \mathbf{A} \mathbf{m},
    \label{eq:linear-problem-g}
\end{equation}

\noindent where $\mathbf{g}(\mathbf{p})$ is the vector containing the measured
field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
masses of the point sources and $\mathbf{A}$ the \emph{Jacobian matrix}, whose
elements can be obtained as:

\begin{equation}
    a_{ij} = G \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|^2},
    \quad \forall \,\, i = 1, \ldots, N
    \quad \forall \,\, j = 1, \ldots, M.
\end{equation}

By solving equation~\ref{eq:linear-problem-g} we can obtain the values of
$\mathbf{m}$ that better reproduce the measured field.
This source distribution along with the fitted masses can be used to predict
gravity values on any point where the potential field has not been measured.

Worth noting that solving equation~\ref{eq:linear-problem-g} is equivalent to
an inversion and thus solving an ill-posed problem by nature due to the
non-uniqueness and the instability of the possible solutions.
Therefore is usually needed to add regularization functions in order to obtain
stable solutions \citep{oliveira2013}.
Moreover there's no limitation on the amount of point sources.
The number of sources can either be equal, less or more than the number of
observation points, leading to well, under or overdetermined linear problem,
respectively.

Add other possible applications to the EQL like RTP or upward continuation.

\subsection{Generalization of equivalent sources}

By definition, any harmonic field $V$ must satisfy the Laplace's equation:

\begin{equation}
    \nabla^2 V = 0.
\end{equation}

The fundamental solution $\psi$ \citep[p.~210]{vladimirov1979} of the harmonic
field $V$ must satisfy:

\begin{equation}
    \nabla_\mathbf{p}^2 \psi(\mathbf{p}, \mathbf{q}) =
        - 4\pi \delta(\mathbf{p}, \mathbf{q})
\end{equation}

\noindent where $\delta(\mathbf{p}, \mathbf{q})$ is the Dirac's delta function
and $\nabla_\mathbf{p}$ symbolize the Nabla operator applied on the
coordinates $\mathbf{p}$.

Assuming that $\psi$ tends to zero when approaching to infinity as boundary
condition, the fundamental solution of any harmonic field can be obtained as
follows \citep{blakely1995}:

\begin{equation}
    \psi(\mathbf{p}, \mathbf{q})
    =
    \int
    \frac{\delta(\mathbf{p}, \mathbf{q})}{|\mathbf{p} - \mathbf{q}|}
    \textrm{d}v
    =
    \frac{1}{|\mathbf{p} - \mathbf{q}|}
    =
    \frac{1}{r}.
\end{equation}

This shows that the Green's function associated with any harmonic field is
equal to one over the Cartesian distance between the evaluation and the source
points.

@@

\begin{equation}
    \textrm{depth} =
        \textrm{depth factor} \cdot \textrm{mean distance}
        + \textrm{static shift}
\end{equation}

\noindent where the \emph{depth factor} and the \emph{static shift} are
parameters and the \emph{mean distance} is the mean distance to the $k$
nearest source neighbours.
